---
title: "Weight Lifting Predictions"
author: "Jacob Townson"
date: "August 4, 2015"
output: html_document
---

# Overview

In this project, I will analyze data taken on the movements of test subjects as they do certain activities. I will use machine learning methods (specifically random forrests) to analyze a large set of data, then use the model created from this to predict the activity that the test subjects were doing in a smaller set of data. Before we begin, we must first read in the data.

```{r}
if(exists('train') == FALSE){
  train <- read.csv('https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv')
}
if(exists('test') == FALSE){
test <- read.csv('https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv')
}
```

# Cleaning the Data

Before making the model, it is important to clean out any unnecessary measurements in the dataset so that the model won't get a false prediction based off of facts that don't matter. In this case, we can assume that time does not affect a persons movements, and also that the "window of time" doesn't matter either. So we must take this out of both the test and train data sets.

```{r}
goodNames <- sapply(test, function(x)!all(is.na(x)))
df <- train[,goodNames]
namesdf <- names(df)
wanted <- namesdf[-c(1,3,4,5,6,7)]
df <- df[,wanted]
lastTest <- test[,goodNames]
namesdf <- names(lastTest)
wanted <- namesdf[-c(1,3,4,5,6,7)]
lastTest <- lastTest[,wanted]
```

Now that our data sets are cleaned up, we may proceed to the rest of the project





